Blum axioms and nondeterministic computation of functions

### 2016-04-20 paper.tex
paper.tex: Fix definition of complexity classes.
paper.tex: Simplify introduction to Blum axioms.

The \emph{complexity} of a computation is how much of a resource
that is invested in that computation~\cite[p.~285]{HopcroftUllman1979}.
For each model of computation and each resource under that model,
we can establish a \emph{complexity measure} concerning that resource.
This section is devoted to formalizing this notion.

Note that the complexity measure must be subordinated to the machine model.
For instance,
in an assembly language,
we could measure the number of \texttt{jump} instructions executed during execution.
This complexity measure makes no sense for Turing machines,
which have no stacks.

Therefore,
we must have an acceptable Gödel numbering $\phi$
to discuss complexity.
As we did with the machine encodings,
we will impose some restrictions on what can be a complexity measure
to be able to manipulate it (at least indirectly).
In our case,
we will use Blum axioms~\cite[p.~324]{Blum1967}.

@@

\begin{definition}
    Given a complexity measure $\Phi$ for an acceptable Gödel numbering $\phi$
    and a total recursive function $f : \mathbb N \to \mathbb N$,
    define the \emph{complexity class} $\mathcal C_\Phi(f)$ by
    (\cite[p.~232]{Kozen2006})
    \begin{equation*}
        \mathcal C_\Phi(f) = \{
            \phi_i \mid \Phi_i(x) \leq f(|x|)\ \text{almost everywhere\footnotemark}
        \}.
    \end{equation*}
    \footnotetext{
        \emph{Almost everywhere} means that the inequality $\Phi_i(x) \leq f(|x|)$
        holds for all but a finite number of different $x$.
    }
\end{definition}

>>>>

The \emph{complexity} of a computation is how much of a resource
that is invested in that computation~\cite[p.~285]{HopcroftUllman1979}.
For each model of computation and each resource under that model,
we can establish a \emph{complexity measure} concerning that resource.
This section is devoted to formalizing this notion.
As we did with the machine encodings,
we will impose some restrictions on what can be a complexity measure
to be able to manipulate it (at least indirectly).
In our case,
we will use Blum axioms~\cite[p.~324]{Blum1967}.

@@

\begin{definition}
    Given a complexity measure $\Phi$ for an acceptable Gödel numbering $\phi$
    and a total recursive function $f : \mathbb N \to \mathbb N$,
    define the \emph{complexity class} $\mathcal C_\Phi(f)$ by
    (\cite[p.~232]{Kozen2006})
    \begin{equation*}
        \mathcal C_\Phi(f) = \{
            \phi_w \mid \Phi(w, x) \leq f(|x|)\ \text{almost everywhere\footnotemark}
        \}.
    \end{equation*}
    \footnotetext{
        \emph{Almost everywhere} means that the inequality $\Phi_i(x) \leq f(|x|)$
        holds for all but a finite number of different $x$.
    }
\end{definition}
